### 2016-03-18 papers.tex
papers.tex: Associate Ben's blast-from-the-past review with the correct paper
Add late submission on ShAIkespeare, Mona, and the Dragon

\addtrack{Full track}{Safety Schools of Thought}
\addpaper
	{Reducing the trusted constituent base with the LCF approach: Hillary, the next 700 elections}
	{Brandon Bohrer, Sol Boucher, and Jos Valdivida}
	{illogical, logic, Hillary, elections, congressional, fuckery, robustness, constituents, unrest, pork-barreling, curtain-closing}
	{SIGBOVIK_2016_paper_25}
	{0cm}
	{}
\addpaper
	{Unprl: Nuprl proof re-evaluation logic}
	{Ryan Kavanagh}
	{proof assistant, Nuprl, The Wizard of Oz, artificial artificial intelligence}
	{SIGBOVIK_2016_paper_11}
	{0cm}
	{}
\addpaper
	{Type-safe friends will never hurt you}
	{Brandon Bohrer}
	{friendship logic, friends, office mates, Cwelf}
	{SIGBOVIK_2016_paper_9}
	{-2cm}
	{}
\addreview{review9}{0cm}

@@

\addtrack{Lamb track}{Languages: Human and... Inhuman}
\addpaper
	{Lambda Doge: A digital canine language}
	{Joshua Suereth}
	{lambda calculus, doge, programming languages}
	{SIGBOVIK_2016_paper_15}
	{0cm}
	{}
\addpaper
	{Making the theoretical possible: the untyped $\lambda$-calculus in C++}
	{Jim McCann}
	{lambda, c++, c++11}
	{SIGBOVIK_2016_paper_23}
	{0cm}
	{}
\addpaper
	{A shortmantout}
	{David Renshaw and Jim McCann}
	{portmanteausteritycoon, hotshots, carthartichokes, sadjustment}
	{SIGBOVIK_2016_paper_13}
	{0cm}
	{}

@@

\addtrack{Cattle track}{Higher-order Research}
\addpaper
	{On the topic of "um..."}
	{Timothy J.\ Parenti}
	{um, best, paper}
	{SIGBOVIK_2016_paper_20}
	{-0.55cm}
	{}
\addpaper
	{SMACK: When research in algorithms goes around in circles}
	{Patrick Lin and Weishuang Linda Xu}
	{algorithms, collider, particle physics}
	{SIGBOVIK_2016_paper_4}
	{-2cm}
	{}
\addpaper
	{A look into the mind of the modern graduate student via telephonic obfuscation}
	{Erik Harpstead \textit{et al.}}
	{comestibility theory, telephonic obfuscation, computer human interaction}
	{SIGBOVIK_2016_paper_6}
	{0cm}
	{}
\addpaper
	{Dinner grant renewal request}
	{From Dr.\ Angus McNabb III to Jim McCann}
	{dinner, dog pictures, naps, napping, nap time, sleeping}
	{SIGBOVIK_2016_paper_14}
	{0cm}
	{}
\addpaper
	{Ode to reviewer two}
	{Anonymous}
	{ode, double-blind review, false politeness, landslide}
	{SIGBOVIK_2016_paper_7}
	{0cm}
	{}
\addreview{review-bestpaper}{0cm}

>>>>

\addtrack{Full track}{Safety Schools of Thought}
\addpaper
	{Reducing the trusted constituent base with the LCF approach: Hillary, the next 700 elections}
	{Brandon Bohrer, Sol Boucher, and Jos Valdivida}
	{illogical, logic, Hillary, elections, congressional, fuckery, robustness, constituents, unrest, pork-barreling, curtain-closing}
	{SIGBOVIK_2016_paper_26}
	{0cm}
	{}
\addpaper
	{Unprl: Nuprl proof re-evaluation logic}
	{Ryan Kavanagh}
	{proof assistant, Nuprl, The Wizard of Oz, artificial artificial intelligence}
	{SIGBOVIK_2016_paper_11}
	{0cm}
	{}
\addpaper
	{Type-safe friends will never hurt you}
	{Brandon Bohrer}
	{friendship logic, friends, office mates, Cwelf}
	{SIGBOVIK_2016_paper_9}
	{-2cm}
	{}
\addreview{review9}{0cm}

@@

\addtrack{Lamb track}{Languages: Human and... Inhuman}
\addpaper
	{Lambda Doge: A digital canine language}
	{Joshua Suereth}
	{lambda calculus, doge, programming languages}
	{SIGBOVIK_2016_paper_15}
	{0cm}
	{}
\addpaper
	{Making the theoretical possible: the untyped $\lambda$-calculus in C++}
	{Jim McCann}
	{lambda, c++, c++11}
	{SIGBOVIK_2016_paper_23}
	{0cm}
	{}
\addpaper
	{ShAIkespeare in the modern age}
	{Abida Haque}
	{Shakespeare, AI, semantic networks, frames, intelligence}
	{SIGBOVIK_2016_paper_25}
	{0cm}
	{}
\addpaper
	{A shortmantout}
	{David Renshaw and Jim McCann}
	{portmanteausteritycoon, hotshots, carthartichokes, sadjustment}
	{SIGBOVIK_2016_paper_13}
	{0cm}
	{}

@@

\addtrack{Cattle track}{Higher-order Research}
\addpaper
	{On the topic of "um..."}
	{Timothy J.\ Parenti}
	{um, best, paper}
	{SIGBOVIK_2016_paper_20}
	{-0.55cm}
	{}
\addreview{review-bestpaper}{0cm}
\addpaper
	{SMACK: When research in algorithms goes around in circles}
	{Patrick Lin and Weishuang Linda Xu}
	{algorithms, collider, particle physics}
	{SIGBOVIK_2016_paper_4}
	{-2cm}
	{}
\addpaper
	{A look into the mind of the modern graduate student via telephonic obfuscation}
	{Erik Harpstead \textit{et al.}}
	{comestibility theory, telephonic obfuscation, computer human interaction}
	{SIGBOVIK_2016_paper_6}
	{0cm}
	{}
\addpaper
	{Dinner grant renewal request}
	{From Dr.\ Angus McNabb III to Jim McCann}
	{dinner, dog pictures, naps, napping, nap time, sleeping}
	{SIGBOVIK_2016_paper_14}
	{0cm}
	{}
\addpaper
	{Ode to reviewer two}
	{Anonymous}
	{ode, double-blind review, false politeness, landslide}
	{SIGBOVIK_2016_paper_7}
	{0cm}
	{}
